---
title: "R Data Analysis Project"
---

Data from Kaggle, 'Vehicle dataset: Used Cars data from websites'

Column description
name: car name
year: manufactured year
selling_price: the price when the car was sold (currency: INR, Indian Rupee)
km_driven: mileage but in km unit
fuel: type of fuel the car consumes
seller_type: how the seller sold the car, individual? or dealer?
transmission: the car's transmission type
owner: how many owners were there?

```{r}
library(readxl)
library(tidyr)
library(ggplot2)
library(lattice)
library(caret)
library(fastDummies)
library(car)
library(dplyr)
library(tidyverse)
```

--------------------IMPORT DATA-------------------------------------------------

```{r}
Used_raw = read.csv('Car details v3.CSV')
```

```{r}
Used_raw[1:5,]
```


--------------------DATA CLEANING-----------------------------------------------

```{r}
summary(Used_raw)
```

```{r}
Used_raw <- drop_na(Used_raw)
```

```{r}
Used_raw <- Used_raw %>% mutate(mil_km = parse_number(mileage),
                    eng_cc = parse_number(engine),
                    max_pow = parse_number(max_power)
                    )
Used_raw <- drop_na(Used_raw)
```
```{r}
Used_raw <- Used_raw[, -c(1,9,10,11,12)]
```

```{r}
table(Used_raw$km_driven)
```
```{r}
table(Used_raw$mil_km)
```
SHOULD REMOVE POSSIBLE OUTLIERS
km_driven: = 1 too low
km_driven: > 1,000,000 too high
mileage in km: = 0 doesn't make sense
mileage in km: = 42 looks too high comare to other numbers

```{r}
Used_raw <- filter(Used_raw, !km_driven == 1,
       !km_driven > 1000000,
       !mil_km == 0,
       !mil_km == 42)
```

```{r}
write.csv(Used_raw, 'df_for_shiny.csv', row.names = FALSE)
```

```{r}
colnames(Used_raw[,-c(2)])
```

--------------------VISUALIZATION-----------------------------------------------
```{r}
ggplot(Used_raw, aes(selling_price)) +
  geom_histogram(binwidth = 500000, colour = 'black', fill = 'white') +
  labs(title = 'selling price') +
  xlab('selling price(INR)')
```
```{r}
ggplot(Used_raw, aes(log(selling_price))) +
  geom_histogram(binwidth = 0.5, colour = 'black', fill = 'white') +
  labs(title = 'log_selling price') +
  xlab('log of selling price')
```

```{r}
ggplot(Used_raw, aes(fuel, log(selling_price), fill=fuel)) +
  geom_boxplot() +
  labs(title = "fuel vs selling price",) +
  ylab('log of selling price')
```
```{r}
ggplot(Used_raw, aes(year)) +
  geom_histogram(binwidth = 1, colour = 'black', fill = 'white') +
  labs(title = 'histogram of year') +
  scale_x_continuous(breaks = 1990:2020) +
  theme(axis.text.x = element_text(angle = 90))
```
```{r}
ggplot(Used_raw, aes(year,log(selling_price))) +
  geom_point() +
  labs(title = 'year vs selling price') +
  ylab('log of selling price')
```

```{r}
ggplot(Used_raw, aes(km_driven, log(selling_price))) +
  geom_point(alpha=0.2) +
  labs(title = 'km_driven vs selling price') +
  ylab('log of selling price')
```

```{r}
ggplot(Used_raw, aes(seller_type, log(selling_price), fill = seller_type)) +
  geom_boxplot() +
  labs(title = 'seller type vs selling price') +
  ylab('log of selling price')
```
```{r}
ggplot(Used_raw, aes(transmission, log(selling_price), fill = transmission)) +
  geom_boxplot() +
  labs(title = 'transmission vs selling price') +
  ylab('log of selling price')
```

```{r}
ggplot(Used_raw, aes(owner, log(selling_price))) +
  geom_bar(aes(fill = seller_type), stat="identity", position = 'dodge') +
  theme(axis.text.x = element_text(angle = 30)) +
  labs(title = 'owner vs selling price')
```

```{r}
ggplot(Used_raw, aes(mil_km, log(selling_price))) +
  geom_point() +
  labs(title = 'mileage vs selling price') +
  ylab('log of selling price')
```
```{r}
ggplot(Used_raw, aes(eng_cc, log(selling_price))) +
  geom_point() +
  labs(title = 'engine cc vs selling price') +
  ylab('log of selling price')
```
```{r}
ggplot(Used_raw, aes(max_pow, log(selling_price))) +
  geom_point() +
  labs(title = 'max power vs selling price') +
  ylab('log of selling price')
```


--------------------TRAIN TEST SPLIT--------------------------------------------

```{r}
set.seed(71)
trainIndex_f <- createDataPartition(Used_raw[,'selling_price'], p=.70,
                                  list = FALSE,
                                  times = 1)
train_idx_f <- Used_raw[trainIndex_f,]
test_idx_f <- Used_raw[-trainIndex_f,]
```


--------------------Processing and Modeling-------------------------------------

```{r}
Used_numeric <- dummy_cols(train_idx_f, select_columns = c('fuel', 'seller_type', 'transmission', 'owner'),
                           remove_selected_columns = TRUE,
                           remove_first_dummy = TRUE)
```

```{r}
corr_diesel <- data.frame(cor(Used_numeric))['fuel_Diesel']
corr_diesel$feature <- rownames(corr_diesel)
```
```{r}
ggplot(corr_diesel, aes(feature, fuel_Diesel, fill=feature)) + 
  geom_bar(stat = 'identity') +
  labs(title = 'correlation of fuel_Diesel') +
  theme(axis.text.x = element_text(angle = 90))
```



```{r}
train_lm <- lm(log(selling_price) ~ . , data = Used_numeric)
summary(train_lm)
```
```{r}
data.frame(vif(train_lm))
```

--------------------ADJUST DUMMIFY COLUMN---------------------------------------
```{r}
Used_num2 <- dummy_cols(train_idx_f, select_columns = c('fuel', 'seller_type', 'transmission', 'owner'),
                           remove_selected_columns = TRUE)
Used_num2 <- Used_num2[,-c(9, 12, 15, 17)]
```

```{r}
train_lm2 <- lm(log(selling_price) ~ . , data = Used_num2)
summary(train_lm2)
```

```{r}
data.frame(vif(train_lm2))
```

```{r}
Used_final <- Used_num2[,-c(6, 9, 12)]
```

```{r}
train_lm3 <- lm(log(selling_price) ~ . , data = Used_final)
summary(train_lm3)
```

```{r}
data.frame(vif(train_lm3))
```

```{r}
Used_final2 <- Used_final[,-c(5)]
```

```{r}
train_lm4 <- lm(log(selling_price) ~ . , data = Used_final2)
summary(train_lm4)
```

```{r}
data.frame(vif(train_lm4))
```



```{r}
AIC(train_lm,
    train_lm2,
    train_lm3,
    train_lm4)
BIC(train_lm,
    train_lm2,
    train_lm3,
    train_lm4)
```



--------------------USE THE MODEL 'train_lm4' TO TEST---------------------------
```{r}
Used_test <- dummy_cols(test_idx_f, select_columns = c('fuel', 'seller_type', 'transmission', 'owner'),
                           remove_selected_columns = TRUE)
Used_test <- Used_test[,-c(9, 12, 15, 17)]
```
```{r}
Used_test <- Used_test[,-c(6, 9, 12)]
Used_test <- Used_test[,-c(5)]
```




```{r}
x_test_f <- Used_test[,-2]
Used_test$predict <- predict(train_lm4, x_test_f)
sqrt(sum(log(Used_test$selling_price)-Used_test$predict)^2/nrow(Used_test)) #standard error
plot(log(Used_test$selling_price)-Used_test$predict)
```

```{r}
Used_test$diff <- log(Used_test$selling_price)-Used_test$predict
ggplot(Used_test, aes(diff)) +
  geom_histogram(binwidth = 0.2, colour = 'black', fill = 'white') +
  labs(title = 'predict vs test') +
  xlab('difference')
```


```{r}
PRESS <- function(linear.model) {
  #' calculate the predictive residuals
  pr <- residuals(linear.model)/(1-lm.influence(linear.model)$hat)
  #' calculate the PRESS
  PRESS <- sum(pr^2)
  
  return(PRESS)
}

pred_r_squared <- function(linear.model) {
  #' Use anova() to get the sum of squares for the linear model
  lm.anova <- anova(linear.model)
  #' Calculate the total sum of squares
  tss <- sum(lm.anova$'Sum Sq')
  # Calculate the predictive R^2
  pred.r.squared <- 1-PRESS(linear.model)/(tss)
  
  return(pred.r.squared)
}

```

```{r}
pred_r_squared(train_lm4)
```


